Community-Conditioned Language Models

### 2020-11-12 paper/paper.tex
oopses
comment/message

Reddit is divided into forums called \textit{subreddits}, 
which are typically organized around a topic of interest. 
Users create \textit{posts}, which consist of a link, image, 
or text, along with a \emph{comment} section. 
Comments are threaded: a comment can be made directly on a post,
or appear as a reply to another comment.

Our dataset includes comments from \num{46} subreddits, 
randomly selected from the set of all forums 
with at least \num{15000} comments per month for each month
in the three years between 2015 and 2017. 
We initially selected \num{50} subreddits, 
but excluded four of them from further analysis: 
two which were primarily non-English and two with particularly\jp{quantify?} short average comment lengths.
Each community corpus consist of \num{50000} randomly selected comments from the year 2015.

Comments were preprocessed as follows: 
We excluded the content of block quotes, code blocks, and tables.
We removed any markup (formatting) commands from the remaining text, extracting only rendered text.
We tokenized the comments using the default English model for the SpaCy tokenizer Version 2.2.3 \citep{Honnibal2017}
and lower-cased all tokens.

@@

We use a vocabulary size of \num{40000} tokens, including a special out-of-vocabulary token.
The vocabulary consisted of the most frequent tokens at the comment level,
meaning that we only counted each token once per comment.
The main reason for this choice was to avoid over-counting otherwise rare tokens that were spammed
many times in a single comment.

We trained the models on a simple left-to-right\jp{I don't think that this applies for the transformer model} language modeling task 
with cross entropy loss over the vocabulary 
and AdamW \citep{Loshchilov2019} optimization, with an inital learning rate of \num{0.001}.
We used a batch size of \num{256} and a maximum sequence length of \num{64} tokens, truncating longer comments (16.8\% of comments were longer than \num{64} tokens).
During training, a dropout rate of $0.1$ was applied between encoder layers 
and after each linear layer.

@@

We now turn our interest to language-model-based community classifiers
(LMCC). Given a comment $m$, and LMCC gives the probability that it
belongs in a community $c_i$ Using the Bayes theorem, we can turn a
CCLM into a LMCC. Indeed, the probability that a given comment $m$
belongs to a community $c_i$ can be calculated as follows:
\[P(c=c_i | m) = P(m | c_i)\frac {P(m)} {P(c=c_i)}\]
In the above,
$P(c=c_i)$ is the frequency of community $c_i$ in the dataset, and
$P(m | c_i)$ is given by the CCLM. $P(m)$ is our normalisation factor, which can be set so that
\[\sum_i P(c=c_i | m) = 1\].

Knowing that $m$ \emph{actually} comes from community $c_j$, we can
measure the precision our classifier, as a confusion matrix $C$,
which can be calculated as follows for a given set of comment (TODO: what set exactly?)
\[C_{ij} = average_{\{m ∈ Posts(c_j)\}}(P(c=c_i | m))\].

@@

While the confusion matrices provide a lot of insight, they are
somewhat \emph{too} fine-grained. For this reason, we will be
interested in confusing the comments from community $c_j$ are to the
LMCC. For this purpose, we consider the perplexity of the LMCC for a
comment coming from community $j$, defined as the exponential of the
entropy of the distribution \(D_j\), which is the (discrete)
probability distribution of predicted community for a random comment from
$c_j$. $D_j$ is simply the $j$th row in \(C\), and so we obtain the formula:
\[Ppl_j = e^{-\sum_i C_{ij} log(C_{ij})}\]

@@

% We see a positive correlation: this suggests that the more stable a
% community is, the more difficult it is to identify comment as coming
% from it. What this suggests is that stable communities tend to use a
% varied and standard, subset of English, while unstable communities
% resort to more formulaic language. This may suggests that to 'fit' in an
% unstable community, one must use more obvious linguistic cues than in
% a stable community. In fact, it is reasonable to think that a new
% member will ostensibly use community-specifc language, but once
% established in a community, a member would tend not to do so.

>>>>

Reddit is divided into forums called \textit{subreddits}, 
which are typically organized around a topic of interest. 
Users create \textit{posts}, which consist of a link, image, 
or text, along with a \emph{comment} section. 
Comments are threaded: a comment can be made directly on a post,
or appear as a reply to another comment.
%
Hereafter we refer to such comments as ``messages'', to match our
convention in mathematical formulas: the letter $c$ stands for a
community, and $m$ stands for a message.

Our dataset includes messages from \num{46} subreddits, 
randomly selected from the set of all forums 
with at least \num{15000} messages per month for each month
in the three years between 2015 and 2017. 
We initially selected \num{50} subreddits, 
but excluded four of them from further analysis: 
two which were primarily non-English and two with particularly\jp{quantify?} short average message lengths.
Each community corpus consist of \num{50000} randomly selected messages from the year 2015.

Messages were preprocessed as follows: 
We excluded the content of block quotes, code blocks, and tables.
We removed any markup (formatting) commands from the remaining text, extracting only rendered text.
We tokenized the messages using the default English model for the SpaCy tokenizer Version 2.2.3 \citep{Honnibal2017}
and lower-cased all tokens.

@@

We use a vocabulary size of \num{40000} tokens, including a special out-of-vocabulary token.
The vocabulary consisted of the most frequent tokens at the message level,
meaning that we only counted each token once per message.
The main reason for this choice was to avoid over-counting otherwise rare tokens that were spammed
many times in a single message.

We trained the models on a simple left-to-right\jp{I don't think that this applies for the transformer model} language modeling task 
with cross entropy loss over the vocabulary 
and AdamW \citep{Loshchilov2019} optimization, with an inital learning rate of \num{0.001}.
We used a batch size of \num{256} and a maximum sequence length of \num{64} tokens, truncating longer messages (16.8\% of messages were longer than \num{64} tokens).
During training, a dropout rate of $0.1$ was applied between encoder layers 
and after each linear layer.

@@

We now turn our interest to language-model-based community classifiers
(LMCC). Given a message $m$, and LMCC gives the probability that it
belongs in a community $c_i$ Using the Bayes theorem, we can turn a
CCLM into a LMCC. Indeed, the probability that a given message $m$
belongs to a community $c_i$ can be calculated as follows:
\[P(c=c_i | m) = P(m | c_i)\frac {P(m)} {P(c=c_i)}\]
In the above,
$P(c=c_i)$ is the frequency of community $c_i$ in the dataset, and
$P(m | c_i)$ is given by the CCLM. $P(m)$ is our normalisation factor, which can be set so that
\[\sum_i P(c=c_i | m) = 1\].

Knowing that $m$ \emph{actually} comes from community $c_j$, we can
measure the precision our classifier, as a confusion matrix $C$,
which can be calculated as follows for a given set of messages (TODO: what set exactly?)
\[C_{ij} = average_{m \in Messages(c_j)}(P(c=c_i | m))\].

@@

While the confusion matrices provide a lot of insight, they are
somewhat \emph{too} fine-grained. For this reason, we will be
interested in confusing the messages from community $c_j$ are to the
LMCC. For this purpose, we consider the perplexity of the LMCC for a
message coming from community $j$, defined as the exponential of the
entropy of the distribution \(D_j\), which is the (discrete)
probability distribution of predicted community for a random message from
$c_j$. $D_j$ is simply the $j$th row in \(C\), and so we obtain the formula:
\[Ppl_j = e^{-\sum_i C_{ij} log(C_{ij})}\]

@@

% We see a positive correlation: this suggests that the more stable a
% community is, the more difficult it is to identify message as coming
% from it. What this suggests is that stable communities tend to use a
% varied and standard, subset of English, while unstable communities
% resort to more formulaic language. This may suggests that to 'fit' in an
% unstable community, one must use more obvious linguistic cues than in
% a stable community. In fact, it is reasonable to think that a new
% member will ostensibly use community-specifc language, but once
% established in a community, a member would tend not to do so.
